\color{red}{The Marshall and Olkin-G and Gamma-G family of distributions: properties and applications }

### 2022-05-30 paper/carta_resposta/letter_answers.tex
Add tex

\emph{Response}:
{\color{red} Indeed, the way in which the application section was introduced suggests that a forced attempt was made to fit the $G\sim Weibull$ model as an adequate distribution to the datasets, thus clashing with the distribution considered in the simulations. To eliminate some ambiguity, we chose to extend the simulations studies, where we now also include the MOGa-Weibull distribution.

Furthermore, the simulations of the MOGa-Dagum distribution were redone, considering that the current hardware is not 
the same as that one we used at the time of submission.

The Monte-Carlo simulations were performed in parallel, using the package \textbf{parallel} of the \texttt{R} language, in which the pseudo-random number generator considered for a processing with thread division was the L'Ecuyer-CMRG (see \url{https://pubsonline.informs.org/doi/abs/10.1287/opre.47.1.159} and \url{https://pubsonline.informs.org/doi/abs/10.1287/opre.50.6.1073.358}. As this generator depends on a fixed seed and also on the number of threads, which in turn depends on the hardware used, this was the other reason that led us to redo all the simulations.}

@@

\textcolor{red}{The \textbf{AdequacyModel} package was developed 
by one of the authors of this paper and it was published at \url{https://journals .plos.org/plosone/article?id=10.1371/journal.pone.0221487}. 
A code inspection of the \texttt{goodness.fit} function can be done by looking at the link   \href{https://github.com/prdm0/AdequacyModel/blob/master/R/goodness.fit.R}{link} on GitHub, where it is hosted the development versioning of the package.}

@@

\emph{Response}:
\textcolor{red}{Thanks for the suggestion. This suggestion was implemented.}

@@

\emph{Response}: \textcolor{red}{Missing.}

@@

\begin{itemize}
\item
  \begin{enumerate}
  \def\labelenumi{(\roman{enumi})}
  \tightlist
  \item
    \textcolor{red}{Really, the title of the paper was no good. We changed to \textbf{The Marshall and Olkin-Gamma-G family of distributions: properties and applications}. We believe that the title now clarifies the paper's proposal better. It is worth mentioning that the new title is very consistent with the sequential application of the MO family to the baseline Gamma-G.}
  \end{enumerate}
\item
  \begin{enumerate}
  \def\labelenumi{(\roman{enumi})}
  \setcounter{enumi}{1}
  \tightlist
  \item
    \textcolor{red}{Done. Thanks for the suggestion.}
  \end{enumerate}
\item
  \begin{enumerate}
  \def\labelenumi{(\roman{enumi})}
  \setcounter{enumi}{2}
  \tightlist
  \item
    \textcolor{red}{Thanks for this point. The presentation of the tables was reorganized.}
  \end{enumerate}
\item
  \begin{enumerate}
  \def\labelenumi{(\roman{enumi})}
  \setcounter{enumi}{3}
  \tightlist
  \item
    \textcolor{red}{Thanks for the suggestion. We chose to put the code for the simulations in a repository on GitHub. Thus, we considerably reduced the number of pages in the article and made it easier for readers of the material to reuse the code. With the code on GitHub it is also possible to verify the implementation and validate the simulations obtained. To access the codes, see the link 
    \url{https://github.com/prdm0/MOGG/tree/master/code/simulations}}.
  \end{enumerate}
\end{itemize}

>>>>

\emph{Response}:
{\color{red} Indeed, the way in which the application section was introduced suggests that a forced attempt was made to fit the $G\sim Weibull$ model as an adequate distribution to the datasets, thus clashing with the distribution considered in the simulations. We chose to extend the simulation studies to eliminate some 
ambiguity, where we now also include the MOGa-Weibull distribution.

Furthermore, the simulations of the MOGa-Dagum distribution were redone by considering that the current hardware is not 
the same as that one we used at the time of submission.

The Monte-Carlo simulations were performed in parallel using 
the  \textbf{parallel-}package of the \texttt{R} language, in which the pseudo-random number generator considered for a processing with thread division was the L'Ecuyer-CMRG (see \url{https://pubsonline.informs.org/doi/abs/10.1287/opre.47.1.159} and \url{https://pubsonline.informs.org/doi/abs/10.1287/opre.50.6.1073.358}. As this generator depends on a fixed seed and also on the number of threads, which in turn depends on the hardware used, this was the other reason that led us to redo all the simulations.}

@@

\textcolor{red}{The \textbf{AdequacyModel} package was developed 
by one of the authors of this paper and it was published at \url{https://journals .plos.org/plosone/article?id=10.1371/journal.pone.0221487}. 
A code inspection of the \texttt{goodness.fit} function can be done by looking at the    \href{https://github.com/prdm0/AdequacyModel/blob/master/R/goodness.fit.R}{link} on GitHub, where it is hosted the development versioning of the package.}

@@

\emph{Response}:
\textcolor{red}{Thanks for the suggestion. It was implemented.}

@@

\emph{Response}: \textcolor{red}{We noticed the need to modify the simulations. So, we extended the simulations to the MOGa-Weibull family to be adopted in the data applications. We also add 
the \texttt{R} code on GitHub (see \url{https://github.com/prdm0/MOGG}) for easy checking 
and reuse by readers of the paper.}

@@

\begin{itemize}
\item
  \begin{enumerate}
  \def\labelenumi{(\roman{enumi})}
  \tightlist
  \item
    \textcolor{red}{Really, the title of the paper was no good. Then, we changed to \textbf{``The Marshall and Olkin-Gamma-G family of distributions: properties and applications''}. We believe that the title now clarifies the paper's proposal better. It is worth mentioning that the new title is very consistent with the sequential application of the MO family to the baseline Gamma-G class.}
  \end{enumerate}
\item
  \begin{enumerate}
  \def\labelenumi{(\roman{enumi})}
  \setcounter{enumi}{1}
  \tightlist
  \item
    \textcolor{red}{Done. Thanks for the suggestion.}
  \end{enumerate}
\item
  \begin{enumerate}
  \def\labelenumi{(\roman{enumi})}
  \setcounter{enumi}{2}
  \tightlist
  \item
    \textcolor{red}{Thanks for this point. The presentation of the tables was reorganized.}
  \end{enumerate}
\item
  \begin{enumerate}
  \def\labelenumi{(\roman{enumi})}
  \setcounter{enumi}{3}
  \tightlist
  \item
    \textcolor{red}{Thanks for the suggestion. We chose to put the code for the simulations in a repository on GitHub. Thus, we considerably reduced the number of pages in the article and made it easier for readers of the material to reuse the code. With the code on GitHub it is also possible to verify the implementation and validate the simulations obtained. To access the codes, see the link 
    \url{https://github.com/prdm0/MOGG/tree/master/code/simulations}}.\\\\
  \end{enumerate}
\end{itemize}
